A Comparison of Graph Processing Systems

### 2020-09-19 documentation/paper/sections/overview/overview.tex
kleine fixes von der Rückmeldung und Polymer Overview
updatet gemini and push-pull + reorderd frameworks according to dependencies
framework overview introduction

\section{Overview}
We start with a short overview describing functionality and characteristics of each framework, followed by their required input data formats.

//
\subsection{Galois and Gluon}
\input{sections/overview/galois}

>>>>

\section{Framework Overview}
The following paragraphs is a short overview describing functionality and characteristics of several state-of-the-art graph processing frameworks.
All of the described frameworks are part of our testing.
\todo

\subsection{Galois and Gluon}
\input{sections/overview/galois}
